%!TEX root=cs580S2014-assignment9.tex
% mainfile: cs580S2014-assignment9.tex 
\input{580pre.tex}
\usepackage[compact]{titlesec}

\begin{document}

\MYTITLE{Assignment 10\\{\em On Being a Scientist}, {\em Bugs in Writing}\\
Pr\'{e}cis and Bug Report due Friday, 13 February}
\MYHEADERS{Assignment 10}{Due Fri., 13 Feb.}

\subsection*{Part 1: Write a Pr\'{e}cis}

Read pages 1--14 of the book {\em On Being a Scientist} and write a short, half-page pr\'{e}cis of this material, using
\LaTeX; remember, you must precisely summarize the essential points of this reading.

\subsection*{Part 2: Create a ``Bug Report''}
Read segments 7, 49, 77, 80, and 129 of {\em Bugs in Writing} (BIW). 
In a separate section of the same \LaTeX\ document, create a
``bug report'': for each
of these topics, provide an example (different from any in the {\em BIW}
book, on a topic
related to computer science) of a ``bad'' or ``ugly'' usage, then show
how it would be corrected to form a ``good'' or (preferably) ``splendid''
sentence.

If you can identify a faulty sentence from one of your own papers (submitted
for this course or another computer science course), that would be ideal---you
    are learning to edit yourself!
If not, see if you can locate a bug from a reputable publication or
Web site. If neither of these is possible, you may compose your own
original example.

Always identify the source of any quotations, even if it is from one of your
own papers.

\subsection*{Instructions and Reminders}

Submit a printed copy of your pr\'{e}cis and bug report at the beginning of class on Friday, 13 February. Be prepared to
take part in a class discussion of the contents of the assigned chapters in both books.

Remember that in this and all other assignments submitted for CMPSC 580, you are expected to adhere to professional
standards of writing and formatting. As you are writing and revising, please pay attention to grammar, spelling, style,
and formatting conventions.

{\large\color{black}\textbf{\textit{Work together!}}} Remember, you are all part of a research group and as such you
should collaborate, read and critique one anothers' work, brainstorm ideas, seek advice from others in the class, and offer
help when you are able to provide it---while also adhering to the Honor Code.

\end{document}
