%!TEX root=cs580S2015-survey.tex
% mainfile: cs580S2015-survey.tex 
\input{580pre}
\begin{document}
\MYTITLE{Survey of Interests}
\MYHEADERS{Survey of Interests}{}

Please provide answers in as much detail as possible. If there is insufficient
room on the survey for you to neatly write your answers, create an electronic
document to hold your responses.

\begin{enumerate}
\item
Which computer science course that you've taken, either 
at Allegheny or elsewhere, has had the most appeal to 
you and why?  Identify specific topics in this course 
that were of interest to you and why you liked them.

\vspace{1.5in}

\item
What topic in computer science would you most like to learn more about,
and what steps would you take to learn about it if you had to try to 
learn it on your own? (Be as specific as possible---e.g., do you know names
of people who are involved in this area, or are you familiar with
publications that deal with this area?)

\vspace{1.5in}

\item
Do you read any computer-related publications (including 
online publications or newsgroups) on a regular basis? 
Name them and describe their content.  If you know the 
URL for an online publication that you've named, provide 
that, too 
%(to enter a URL in \LaTeX, use \verb$\url{...}$, 
%e.g., \verb$\url{cs.allegheny.edu/~rroos}$).

\vspace{1.5in}

\item
Have you written any complicated computer programs that 
were either ``just for fun'' or for some purpose other 
than meeting a course or a job requirement? Give details.

\vspace{1.5in}

\item
Have you implemented or installed any computer-related 
systems ``just for fun'' or for some purpose other than 
meeting a course or a job requirement? Give details.

\vspace{1.5in}

\item
Of the following activities, which ones do you enjoy? Which ones do think
you do well? Elaborate on your answers; free-associate if you'd like; 
use additional pages for your response.
\begin{itemize}
\item Writing code that meets someone else's
requirements and specifications
\item Writing code to solve problems that you've come up with on your own 
\item Tracking down information about a topic that's of interest to you
\item Reading computer-related articles in magazines, either
paper or online
\item Explaining computer-related concepts to other people
\item Building or customizing your own computer hardware
\item Something else? What?
\end{itemize}

\newpage

\item
What are your greatest strengths or most useful skills 
with respect to proposing and writing a senior thesis?

\vspace{1.5in}

\item
What are the greatest weaknesses or gaps in your knowledge 
or skills that might hinder you in proposing and writing 
a senior thesis?

\vspace{1.5in}

\item
Propose at least one (and preferably several) concrete 
improvements in your study or work habits that you think 
will improve your chances of doing well in both CMPSC 580 
and in your senior thesis. By ``concrete'' I mean things 
that can be unambiguously measured to show clear evidence of
improvement.

\vspace{1.5in}

\item
Do you have a specific senior project topic in mind already? If so,
briefly describe it.

\end{enumerate}

\end{document}
