%!TEX root=cs580S2015-assignment2.tex
% mainfile: cs580S2015-assignment2.tex 

\input{580pre}
\begin{document}
\MYTITLE{Assignment 2\\Introduction to Research in Computer Science\\Due 23 January 2015}
\MYHEADERS{Introduction to Research in Computer Science}{Due 23 January 2015}

The goal of this assignment is to help you better understand the key characteristics of the discipline of computer
science. To achieve this goal, you should read the paper ``Computing as a Discipline'', by Peter J. Denning et.\ al.\
and write a one-page paper review.

To better grasp how to read this first paper, you should study the article ``How to Read a Paper'' by S.\ Keshav
and learn more about the author's three-pass approach to reading research in computer science. Then, you should examine
``Reading a Computer Science Research Paper'' by Philip W.L.\ Fong and learn how to write a paper review that contains
sections normally called ``summary'', ``critique'', and ``synthesis''. For the two papers mentioned in this paragraph,
you should write a one paragraph response to each. In addition to making other relevant points, you must comment on
the strengths and weaknesses of the approaches proposed by Keshav and Fong.

Although Fong describes a multiple-page review of a research paper, for this course you will always be asked to write a
one-page paper review. At minimum, your review should contain one paragraph for the standard sections of summary,
critique, and synthesis. As long as your review fits onto one page, you may add other points you deem to be important.
Your writing for this assignment---and all other assignments in this course---should be scientific, precise, and formal.

For now, you may write the content required by this assignment using any appropriate approach to text processing and
formatting.  However, in future assignments, students will be responsible for writing all of their documents using the
\LaTeX\ text processing language. Students who already know how to program in \LaTeX\ are encouraged to use it to
prepare their response to this assignment. You may talk with the course instructor during office hours if you are not
already familiar with \LaTeX\ and you would like to learn how to use it to finish your work for this assignment.






\end{document}
