%!TEX root=cs580S2015-assignment19.tex
% mainfile: cs580S2015-assignment19.tex

\input{580pre.tex}
\usepackage[compact]{titlesec}

\begin{document}

\MYTITLE{Assignment 19\\{\em On Being a Scientist}, {\em Bugs in Writing}\\
Pr\'{e}cis and Bug Report due Friday, 27 March}
\MYHEADERS{Assignment 18}{Due Fri., 27 March.}

\subsection*{Part 1: Write a Pr\'{e}cis}

Focusing on issues related to research misconduct, please read pages 15--24 of the book {\em On Being a Scientist} and write a short,
half-page pr\'{e}cis of this material, using \LaTeX.

\subsection*{Part 2: Create a ``Bug Report''}

Read segments 8, 21, 27, 60, and 149 of {\em Bugs in Writing} (BIW).  In a separate section of the same \LaTeX\
document, create a ``bug report'': for each of these topics, provide an example (different from any in the {\em BIW}
book, on a topic related to computer science) of a ``bad'' or ``ugly'' usage, then show how it would be corrected to
form a ``good'' or (preferably) ``splendid'' sentence.

If you can identify a faulty sentence that fit the segments 8, 21, 27 and 60 from one of your own papers (submitted for
this course or another computer science course), that would be ideal---you are learning to edit yourself!  If not, see
if you can locate a bug from a reputable publication or Web site, or for example publications we have read for this
module. If neither of these is possible, you may compose your own original example. Also give a personal example of the
writer's block, or if you have never had one, simply explain what a writer's block is.

Always identify the source of any references, even if it is from one of your own papers.

\subsection*{Instructions and Reminders}

Submit a printed copy of your pr\'{e}cis and bug report at the beginning of class on Friday, 13 February. Be prepared to
take part in a class discussion of the contents of the assigned chapters in both books.

Remember that in this and all other assignments submitted for CMPSC 580, you are expected to adhere to professional
standards of writing and formatting. As you are writing and revising, please pay attention to grammar, spelling, style,
and formatting conventions.

{\large\color{black}\textbf{\textit{Work together!}}} Remember, you are all part of a research group and as such you
should collaborate, read and critique one anothers' work, brainstorm ideas, seek advice from others in the class, and offer
help when you are able to provide it---while also adhering to the Honor Code.

\end{document}
