\documentclass[letterpaper, 10pt]{article} % for letter size paper 
% 215.9mm × 279.4mm
\usepackage{tikz}

\usepackage[T1]{fontenc}
\usepackage{mathptmx}
\usepackage{amssymb}

\topmargin 0.0in
\setlength{\textwidth} {420pt}
\setlength{\textheight} {630pt}
\setlength{\oddsidemargin} {20pt}
\setlength{\marginparwidth} {72in}

\begin{document}
\pagestyle{empty}

\vspace*{-1.2in}

\noindent
{\bf Your Name:} \hspace*{2in} {\bf Presenter(s):} \hspace*{2in} {\bf Grade:} 

\vspace*{.1in}

\noindent
{\bf Course:} Computer Science 580 Spring 2014

\vspace*{.1in}

\noindent
{\bf Assignment:} 

\vspace*{.1in}

\large{

\begin{center}{\bf Presentation Assignment Evaluation} \end{center}

\begin{enumerate}

\setlength{\itemsep}{1pt}

\item Did the student adhere to the honor code? \hspace*{.05in}  $\Box$ Yes
  \hspace*{.05in} $\Box$ No \hspace*{.05in}  $\Box$ Not Clear

\item Was the presentation delivered at the correct date and
  time? \hspace*{.05in} $\Box$ Yes
  \hspace*{.05in} $\Box$ No

\item Was the presentation properly organized? \hspace*{.05in} $\Box$ Yes
  \hspace*{.05in} $\Box$ No 
%% \\ If no, then how could the organized be
%%   improved?  \underline{\hspace*{2in}}

\item Was the presentation's organization adequately
  communicated? \hspace*{.05in} $\Box$ Yes
  \hspace*{.05in} $\Box$ No

\item Did the presentation accurately describe the
  assigned paper? \hspace*{.05in} $\Box$ Yes
  \hspace*{.05in} $\Box$ No

%% \item Did the slides convey the intended message? \hspace*{.05in}
%%   $\Box$ Yes
%%   \hspace*{.05in} $\Box$ No

\item Does the presentation contain all of the necessary
  components? \hspace*{.05in} $\Box$ Yes
  \hspace*{.05in} $\Box$ No \\ \hspace*{.05in} If no, then what
  components are missing? \vspace*{-.05in}

%\hspace*{.1in}
\begin{itemize}
\renewcommand{\labelitemi}{$\Box$}

\setlength{\itemsep}{.5pt}

\item Introduction and motivation

\item Description of technique 

\item Technical diagrams

\item Program screenshots

\item Mathematical notation

\item Tables of data

\item Data visualizations

\item Results analysis

\item Related work 

\item Conclusion 

\item Future work 

\item Other components of a presentation

\end{itemize}

\item Does the presentation contain spelling mistakes? \hspace*{.05in}
  $\Box$ Yes \hspace*{.05in} $\Box$ No

\item Does the presentation have errors in grammar? \hspace*{.05in}
  $\Box$ Yes \hspace*{.05in} $\Box$ No

\item Does the presentation exhibit poor formatting? \hspace*{.05in}
  $\Box$ Yes \hspace*{.05in} $\Box$ No

\item Did the presenter demonstrate a strong knowledge of the
  paper? \hspace*{.05in} $\Box$ Yes \hspace*{.05in} $\Box$ No

\item Did the presenter convey an enthusiastic attitude? \hspace*{.05in}
  $\Box$ Yes \hspace*{.05in} $\Box$ No

\item Did the presenter regularly make eye contact? \hspace*{.05in}
  $\Box$ Yes \hspace*{.05in} $\Box$ No

\item Did the presenter adequately answer questions? \hspace*{.05in}
  $\Box$ Yes \hspace*{.05in} $\Box$ No

\item Did the presenter adhere to the established time limits? \hspace*{.05in}
  $\Box$ Yes \hspace*{.05in} $\Box$ No

\item Overall, how well did the presenter enhance your understanding
  of the paper and enable you to develop new research ideas?
  \\ \hspace*{.05in} $\Box$ Exceptional \hspace*{.05in} $\Box$
  Good \hspace*{.05in} $\Box$ Average \hspace*{.05in} $\Box$ Poor

\end{enumerate}

}

\begin{tabular}{l}

\begin{minipage}{6in} \hspace*{-.25in} {\bf Additional Comments} \vspace*{.25in} \end{minipage} \\ \hline

\begin{minipage}{6in} \vspace*{.25in} \end{minipage} \\ \hline

\begin{minipage}{6in} \vspace*{.25in} \end{minipage} \\ \hline

\begin{minipage}{6in} \vspace*{.25in} \end{minipage} \\ \hline

\begin{minipage}{6in} \vspace*{.25in} \end{minipage} \\ \hline

\begin{minipage}{6in} \vspace*{.25in} \end{minipage} \\ \hline

%% \begin{minipage}{6in} \vspace*{.25in} \end{minipage} \\ \hline

%% \begin{minipage}{6in} \vspace*{.25in} \end{minipage} \\ \hline

%% \begin{minipage}{6in} \vspace*{.25in} \end{minipage} \\ \hline

%% \begin{minipage}{6in} \vspace*{.25in} \end{minipage} \\ \hline

%% \begin{minipage}{6in} \vspace*{.25in} \end{minipage} \\ \hline

%% \begin{minipage}{6in} \vspace*{.25in} \end{minipage} \\ \hline

%\begin{minipage}{6in} \vspace*{.25in} \end{minipage} \\ \hline

\end{tabular}

\end{document}
