\documentclass[letterpaper, 10pt]{article} % for letter size paper 
% 215.9mm × 279.4mm
\usepackage{tikz}

\usepackage[T1]{fontenc}
\usepackage{mathptmx}
\usepackage{amssymb}

\topmargin 0.0in
\setlength{\textwidth} {420pt}
\setlength{\textheight} {630pt}
\setlength{\oddsidemargin} {20pt}
\setlength{\marginparwidth} {72in}

\begin{document}
\pagestyle{empty}

\vspace*{-1in}

\noindent
{\bf Name:} \hspace*{4.8in} {\bf Grade:} 

\vspace*{.1in}

\noindent
{\bf Course:} Computer Science 580, Spring 2014

\vspace*{.1in}

\noindent
{\bf Assignment:} 

\vspace*{.1in}

\large{

\begin{center}{\bf Writing Assignment Evaluation} \end{center}

\begin{enumerate}

\setlength{\itemsep}{.5pt}

\item Did the student adhere to the honor code? \hspace*{.05in}  $\Box$ Yes
  \hspace*{.05in} $\Box$ No \hspace*{.05in}  $\Box$ Not Clear

\item Was the assignment turned in on time? \hspace*{.05in}  $\Box$ Yes
  \hspace*{.05in} $\Box$ One Week Late \hspace*{.05in} $\Box$ Very
  Late

\item Does the assignment contain all of the required
  deliverables? \hspace*{.05in} $\Box$ Yes
  \hspace*{.05in} $\Box$ No \\ \hspace*{.05in} If no, then what
  deliverables are missing? \vspace*{-.05in}

%\hspace*{.1in}
\begin{itemize}
\renewcommand{\labelitemi}{$\Box$}

\setlength{\itemsep}{.5pt}

\item Informative title

\item Summary section

\item Evaluation section

\item Synthesis section

\item Article abstract

\item Introduction section

\item Related work section

\item Description of technique 

\item Future work section

\item Conclusion section

\item Comprehensive list of references 

\item Technical diagrams

\item Equations and/or other mathematical notation

\item Statement of hypothesis or research question(s)

\item Other types of deliverables

\end{itemize} \vspace*{-.05in}

\item Does the writing contain spelling mistakes? \hspace*{.05in}
  $\Box$ Yes \hspace*{.05in} $\Box$ No

\item Does the writing have errors in grammar? \hspace*{.05in}
  $\Box$ Yes \hspace*{.05in} $\Box$ No

\item Does the writing have incorrect punctuation? \hspace*{.05in}
  $\Box$ Yes \hspace*{.05in} $\Box$ No

\item Does the paper exhibit poor formatting? \hspace*{.05in}
  $\Box$ Yes \hspace*{.05in} $\Box$ No

\item Does the paper violate some of the suggestions in {\em Bugs in
  Writing}? \\ \hspace*{.05in} $\Box$ Yes \hspace*{.05in} $\Box$
  No \hspace*{.05in} $\Box$ Maybe \\ \hspace*{.05in} If yes or maybe,
  then what chapters should the student review? \vspace*{-.05in}

\begin{itemize}
\renewcommand{\labelitemi}{$\blacktriangleright$}

\setlength{\itemsep}{1pt}

\item Chapter(s) \underline{\hspace*{.75in}}

\end{itemize} \vspace*{-.05in}

\item Does the paper violate some of the suggestions in {\em Writing
  for Computer Science}? \hspace*{.05in} $\Box$ Yes \hspace*{.05in}
  $\Box$ No \hspace*{.05in} $\Box$ Maybe \\ \hspace*{.05in} If yes or
  maybe, then what chapters should the student
  review? \vspace*{-.05in}

\begin{itemize}
\renewcommand{\labelitemi}{$\blacktriangleright$}

\setlength{\itemsep}{1pt}

\item Chapter(s) \underline{\hspace*{.75in}}

\end{itemize}

\item Overall, how well did the paper achieve the goals of the assignment?
  \\ \hspace*{.05in} $\Box$ Exceptional \hspace*{.05in} $\Box$
  Good \hspace*{.05in} $\Box$ Average \hspace*{.05in} $\Box$ Poor

\end{enumerate}

}

\begin{tabular}{l}

\begin{minipage}{6in} \hspace*{-.175in} {\bf Additional Comments} \vspace*{.25in} \end{minipage} \\ \hline

\begin{minipage}{6in} \vspace*{.25in} \end{minipage} \\ \hline

\begin{minipage}{6in} \vspace*{.25in} \end{minipage} \\ \hline

%\begin{minipage}{6in} \vspace*{.25in} \end{minipage} \\ \hline

%\begin{minipage}{6in} \vspace*{.25in} \end{minipage} \\ \hline

%\begin{minipage}{6in} \vspace*{.25in} \end{minipage} \\ \hline

%\begin{minipage}{6in} \vspace*{.25in} \end{minipage} \\ \hline

%\begin{minipage}{6in} \vspace*{.25in} \end{minipage} \\ \hline

\end{tabular}

\end{document}
