%!TEX root=cs580S2015-assignment9.tex
% mainfile: cs580S2015-assignment9.tex 
\input{580pre.tex}
\usepackage[compact]{titlesec}

\begin{document}

\MYTITLE{Assignment 9\\Ideas for a Senior Thesis Proposal\\
Part 1 due 5 February 2015\\
Part 2 due 6 February 2015}
\MYHEADERS{Assignment 9}{Due Thu., Fri., 5--8 Feb.}

\subsection*{Part 1: Five Ideas}

Create a short \LaTeX\ document listing (at least) five possible senior thesis ideas that are related in some way to the
topic of software testing and debugging. For each idea, come up with a proposed thesis title and a one- or two-sentence
hypothesis/thesis statement, along with a description of your evaluation metrics and a short overview of the system
that you plan to implement. Hand in a hard copy of this list at the beginning of Thursday morning's class (you might
  want to keep a copy for yourself to refer to during Thursday's discussion).

These do {\em not} have to be ``tightly coupled'' to the subject of software testing and debugging through evolutionary
computation. They do {\em not} have to be of the form ``A testing method to handle \ldots'' or ``A debugging tool to
solve \ldots'' or ``A novel empirical study of EvoSuite \ldots.'' Yet, there should be a clear connection between
your proposed idea and the topic of this module.

It would be ideal if you come up with ideas that are personally of interest to you, but that is not an absolute
requirement. Just try to propose feasible ideas; even if you are not interested in carrying out such a project, perhaps
someone else in the class might find your idea worth pursuing.

During a session that a student will chair, we will discuss these ideas in class. Be prepared to provide further
information about your ideas during this discussion.

\subsection*{Part 2: Lightning Talk and Slides}
For Friday afternoon, prepare a ``lightning talk'' (3--5 minutes), together
with several accompanying Beamer slides, in which you expand upon an
idea for a senior thesis related in some way to 
evolutionary computation.

Submit printed copies of your slides at the beginning of Friday's class.
\end{document}
