%!TEX root=cs580S2015-assignmentfp.tex
% mainfile: cs580S2015-assignmentfp.tex
\input{580pre.tex}
\usepackage{ulem}
\usepackage[compact]{titlesec}

\begin{document}

\MYTITLE{Assignment 25\\Final Project\\
Due Friday, 1 May}
\MYHEADERS{Assignment 25}{Due Fri., 1 May}

As the final assignment for this course, you must complete a project consisting of a poster suitable for presentation
during a department-wide poster session, a five to seven minute in-class presentation that describes your proposed
research, and a ten page final research proposal.

The department-wide poster session will take place on Friday, 24 April, 2015 during the normally scheduled laboratory
session.  Using technical diagrams, screen shots, equations, formal statements of algorithms, and other appropriate
components,  you are responsible for presenting a poster that clearly explains your idea for senior thesis research.
Additionally, your poster should correctly use color and layout to ensure that the idea is presented in a clear and
pleasing manner.

While the course instructors will give you a grade for your poster and your participation in the poster session, all
students in the Department of Computer Science will be invited to provide you with written and oral feedback about both
your proposed work and the poster itself.  By 9 am on the morning of the poster session, please send a PDF of your
poster---that was programmed in \LaTeX---to the course instructor so that it can be printed at a size
suitable for display.  You should now use all feedback from the poster session to refine and extend your final project
presentation and proposal. Please see the course instructor if you have any questions about the poster session.

% talk about the final presentations
The final project presentations will take place in class on Tuesday, 28 April, 2015. Each student is required to give a
presentation about the topic that they plan to investigate for their senior thesis.  Beyond giving a presentation, each
student is responsible for answering questions posed by both the course instructor and the other students in the course.
Please use all of the feedback from the presentation sessions to improve your final project proposal.

% talk about the final proposal
You should write your final proposal using the same \LaTeX\ templates that you have used for the previous module
proposals. This proposal should describe the topic that you plan to investigate for your senior thesis at Allegheny
College. Students are encouraged, although not required, to reuse content from their module proposals as they prepare
their final proposal. If you do incorporate material from a previous proposal into your final proposal, then please
indicate what content was reused at the end of your document. The submitted version of your final proposal should take
into account the feedback that you received during both the poster session and your final presentation. Please see the
course instructors if you have questions about \mbox{this part of the assignment}.

\end{document}
