%!TEX root=cs580S2015-assignment1.tex
% mainfile: cs580S2015-assignment1.tex 

\input{580pre}
\begin{document}
\MYTITLE{Assignment 1\\Assessing Your Interests\\Due 15 January 2015}
\MYHEADERS{Assessing Your Interests}{Due 15 January 2015}

The goal of this assignment is to help you identify where your interests lie
in the area of computer science and then to get you started thinking about
how you can combine those interests into a senior project proposal that
will be exciting and rewarding.

I want you to take a serious look at the past two and a half years,
review your computer science experiences, and think about how you want
to spend the next year and a half.  Think about why you chose to major
in computer science. What would you like to be able to say about your
accomplishments at the end of four years? What do you imagine telling a
potential employer about what you've learned and what you've done with
that knowledge?

I have broken this assignment up into a written and an oral component.

\begin{enumerate}

\item Take the ``Survey of Interests'' (provided as a separate handout). Sit down with another member of the class and
  go through the questions together---interview each other. Help each other try to come up with thoughtful
  answers---perhaps you have shared a class together and you can remind each other of ``aha!'' moments experienced late
  at night in the labs, or of assignments or projects that gave you the greatest satisfaction.

Then fill out your answers (if you do not want to hand-write them on the survey sheets, you may type them into a
separate document using a text editor and a language like \LaTeX\ or Markdown) and bring them to class on Thursday. Be
prepared to share your experiences.

\item
Prepare a short (two-minute) ``lightning talk'' for Thursday in 
which you briefly
describe some aspect of computer science that interests you. Try to 
articulate why it interests you. Explain what more
you would like to learn about this area and, if you can, try
to imagine how you might be able to do this through the senior project you complete next year.


Prepare one slide to show on the screen as you give your lightning talk. It 
needn't be complex or formatted in any particular way. However, it should
include your name, the date, your topic, and something to help focus the
viewer's attention on the topic you've chosen.
\end{enumerate}
\end{document}
